---
title: "Emotions and Psychological Distance Analysis"
author: "Desmond Ong"
date: "February 29, 2016"
output: html_document
---

The following data file accompanies Ong, Goodman, & Zaki, which is in press at Emotion. It contains all the code needed to reproduce the analyses reported in the paper.


```{r preamble, echo=FALSE, message=FALSE}
library(ggplot2)
library(MuMIn) # for getting R^2 values using r.squaredGLMM(), after https://ecologyforacrowdedplanet.wordpress.com/2013/08/27/r-squared-in-mixed-models-the-easy-way/ and following Nakagawa and Schielzeth (2013) and Johnson (2014)

source("http://web.stanford.edu/~dco/common/useful.R")
source("http://web.stanford.edu/~dco/common/processData.R")

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
blackGreyPalette <- c("#000000", "#999999")
cbbwPal <- c("#d8b365","#5ab4ac")
cbbwPal2 <- c("orange","steelblue3")

my_theme <-   theme(legend.position="top",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
```


# Introduction

```{r predictions-figure, fig.width = 8, fig.height = 4.2, echo=FALSE, message=FALSE, warning=FALSE}
library(grid)
predictionsFigDF = data.frame(panel = factor(c(rep("Global\nSelf Enhancement",8), 
                                               rep("Increased Sensitivity",8),
                                               rep("Contextualized\nSelf Enhancement",8)),
                                             levels = c("Global\nSelf Enhancement", "Increased Sensitivity",
                                                        "Contextualized\nSelf Enhancement"),
                                             labels = c("a) Global\nSelf Enhancement", 
                                                        "b) Increased Sensitivity", "c) Contextualized\nSelf Enhancement")),
                              Target = factor(rep(rep(c("Self","Other"),each=4),3),
                                             levels=c("Self", "Other"),
                                             labels=c(" Self    ", " Other ")),
                              PE = rep(c(1,2,3,4),6),
                              attribution = c( c(4,5,6,7), # Self: Simple Bias
                                               c(2,3,4,5), # Other: Simple Bias
                                               c(4,5,6,7), # Self: Increased Sensitivity
                                               c(2.5,4.5,6.5,8.5), # Other Increased Sensitivity
                                               c(4,5,6,7), # Self: Both
                                               c(1,3,5,7)) # Other: Both
                             )

ggplot(predictionsFigDF, aes(x=PE, y=attribution, colour=Target, group=Target, linetype=Target)) + 
  ylab("Judgments of Target's Emotional Valence\n") + xlab("Goodness Of Outcome") + geom_line() + 
  scale_colour_manual(values=blackGreyPalette) +
  facet_wrap( ~ panel, ncol=4, as.table=TRUE, drop=FALSE) +
  scale_y_continuous(breaks=c(2.5, 8.6), labels=c("Negative", "Positive"), limits=c(1,8.5)) +
  scale_x_continuous(breaks=c(1.2, 3.8), labels=c("Worse", "Better"), limits=c(0.8, 4.2)) + theme_bw() +
  theme(legend.position="top", strip.background = element_blank(),
        strip.text = element_text(size=14),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12, angle=90),
        axis.ticks = element_blank(),
        axis.line.x = element_line(colour = "black", size = 0.5),
        axis.line.y = element_line(colour = "black", size = 0.5),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank(),
        panel.border = element_blank(),
       plot.margin = unit(c(0,0.2,0.3,0.2), "cm")) # clockwise from top
 

# saved as pdf 7.5 x 4
# changed to 8 x 4.2
```

Top: Figure 1 in paper.<br>
Predictions. On the vertical axis are attributions of happiness following an outcome, and on the horizontal axes are how “good” or “bad” the outcome is. Overall, happiness attributions should increase with the “goodness” of the outcome. Predictions for attributions to oneself are given in solid lines, while attributions to others are given in dashed lines. (a) Predictions from a simple “happier than average” bias that is context-independent. (b) Predictions from an “increased sensitivity” account: attributions to others are more sensitive to changes in the outcome. (c) Combining both (a) and (b).





#Study 1

```{r study1-self-other, echo=FALSE, messages=FALSE, warning=FALSE}
# Reading in the data.
# The data is in wide form: each participant is appears in 1 row, and each participant responds to 10 trials.
study1.wide <- read.csv('data/study1data.csv', header=T)
# table(study1.wide$firstPerson) ## firstPerson = 1 if they were in the Self Condition, 0 otherwise.
# 102 first peron, 98 third person


# gender 1 = F, 2 = M.


# for Trial specific variables
# "variable.X" is the value of that variable for the X-th trial. So, for example, "happy.1" is the response to "happy" , on the first trial. 
# spinnerID : ID of the particular spinner
# payoff1 : payoff of the lowest value on the wheel
# payoff2 : payoff of the 2nd value on the wheel
# payoff3 : payoff of the highest value on the wheel
# prob1   : probability of the lowest value on the wheel (i.e., size of sector)
# prob1   : probability of the 2nd value on the wheel (i.e., size of sector)
# prob1   : probability of the highest value on the wheel (i.e., size of sector)
# win     : actual amount 'won' on the trial. must be one of (payoff1, payoff2, payoff3)
# winProb : probability that corresponds to the amount won. similarly, must be one of (prob1, prob2, prob3)
# angleProp : angle proportion. ranges from 0 to 1. indicates where in the winning sector the wheel landed on.
#            for example, if win = payoff2 (means that the wheel landed in the 2nd sector), 
#                         then angleProp near 0 means that the wheel landed in the 2nd sector, but very close to the 1st sector. angleProp near 1 means the wheel landed closer to the 3rd sector. 0.5 means it landed equally far from both 1st and 3rd sectors. See previous paper, Ong, Zaki, & Goodman (2015) for more details.
# reactionTime: self-explanatory.


# There are other individual difference variables where the .X just refers to the answer to the X-th item on that questionnaire. For example, RSEArray.4 is the answer to the 4th question on the Rosenberg Self Esteem scale
# measures:
# socComp: some social comparison questions I came up with
# RSE: Rosenberg Self Esteem
# LOTR: Life Orientation Test, Revised
# PHQ: Patient-Health Questionnaire-2
# SINS: Single-Item Narcissm Scale




# this is using a helper function I wrote to convert the data from wide form into long form.
study1 <- processData2(study1.wide,
                        variableList = c("spinnerID", "payoff1", "payoff2", "payoff3", 
                                         "prob1", "prob2", "prob3",
                                         "winChoice", "win", "winProb",
                                         "angleProp", "reactionTime",
                                         "happy", "sad", "anger", "surprise", 
                                         "disgust", "fear", "content", "disapp"), 
                            idVarList = c("workerid", "gender", "age", "firstPerson"),
                            numTrials = 10)

# Calculating Expected Value and Prediction Error
study1$EV = study1$prob1*study1$payoff1 + study1$prob2*study1$payoff2 + study1$prob3*study1$payoff3
study1$PE = study1$win - study1$EV

# Creating this other dummy variable.
study1$thirdPerson = factor(1-study1$firstPerson)

# creating emotion composites
study1$positive = (study1$happy + study1$content)/2
study1$negative = (study1$sad + study1$anger + study1$disgust + study1$disapp)/4
```


```{r study1-figures1, fig.width=6, fig.height=4, echo=FALSE}
ggplot(data=study1, aes(x=PE, y=happy, fill=thirdPerson, color=thirdPerson, linetype=thirdPerson)) + 
  geom_point(position=position_jitter(width=0.25,height=0.25), alpha=0.6) + geom_smooth(method='lm', size=1) +
  theme_bw() + xlab('Prediction Error') + ylab('Happy') + scale_fill_brewer(palette="Set1", name="Experimental\nCondition", breaks=c("0", "1"), labels=c("Self", "Other")) + scale_color_brewer(palette="Set1", name="Experimental\nCondition", breaks=c("0", "1"), labels=c("Self", "Other")) +
  scale_linetype_manual(values=c(1, 2), name="Experimental\nCondition", breaks=c("0", "1"), labels=c("Self", "Other")) + my_theme
# 6 by 4

ggplot(data=study1, aes(x=PE, y=disapp, fill=thirdPerson, color=thirdPerson, linetype=thirdPerson)) + 
  geom_point(position=position_jitter(width=0.25,height=0.25), alpha=0.6) + geom_smooth(method='lm', size=1) +
  theme_bw() + xlab('Prediction Error') + ylab('Disappointment') + scale_fill_brewer(palette="Set1", name="Experimental\nCondition", breaks=c("0", "1"), labels=c("Self", "Other")) + scale_color_brewer(palette="Set1", name="Experimental\nCondition", breaks=c("0", "1"), labels=c("Self", "Other")) +
  scale_linetype_manual(values=c(1, 2), name="Experimental\nCondition", breaks=c("0", "1"), labels=c("Self", "Other")) + my_theme
# 6 by 4
```

Top: Figure 3 in paper.<br>
Participants’ attributions of happiness and disappointment to themselves (in red) and others (blue) as a function of PE. Data points are jittered for visibility, with best linear fits overlaid. 



```{r study1-modeling, echo=FALSE, messages=FALSE}
#####
# Study 1 -- Start Analysis
#####

# Run this part to get the statistics reported in the paper

# interactions
s1model1sum = summary(lmer(happy ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model1RSq = r.squaredGLMM(lmer(happy ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#  s1model1sum$coeff[4,1]
#  s1model1sum$coeff[4,1] - 1.96 * s1model1sum$coeff[4,2]
#  s1model1sum$coeff[4,1] + 1.96 * s1model1sum$coeff[4,2]
#  s1model1sum$coeff[4,3]
#  2*(1-pt(abs(s1model1sum$coeff[4,3]),196))
s1model2sum = summary(lmer(content ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model2RSq = r.squaredGLMM(lmer(content ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#  s1model2sum$coeff[4,1]
#  s1model2sum$coeff[4,1] - 1.96 * s1model2sum$coeff[4,2]
#  s1model2sum$coeff[4,1] + 1.96 * s1model2sum$coeff[4,2]
#  s1model2sum$coeff[4,3]
#  2*(1-pt(abs(s1model2sum$coeff[4,3]),196))
s1model3sum = summary(lmer(sad ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model3RSq = r.squaredGLMM(lmer(sad ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#  s1model3sum$coeff[4,1]
#  s1model3sum$coeff[4,1] - 1.96 * s1model3sum$coeff[4,2]
#  s1model3sum$coeff[4,1] + 1.96 * s1model3sum$coeff[4,2]
#  s1model3sum$coeff[4,3]
#  2*(1-pt(abs(s1model3sum$coeff[4,3]),196))
s1model4sum = summary(lmer(anger ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model4RSq = r.squaredGLMM(lmer(anger ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#  s1model4sum$coeff[4,1]
#  s1model4sum$coeff[4,1] - 1.96 * s1model4sum$coeff[4,2]
#  s1model4sum$coeff[4,1] + 1.96 * s1model4sum$coeff[4,2]
#  s1model4sum$coeff[4,3]
#  2*(1-pt(abs(s1model4sum$coeff[4,3]),196))
s1model5sum = summary(lmer(disgust ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model5RSq = r.squaredGLMM(lmer(disgust ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#  s1model5sum$coeff[4,1]
#  s1model5sum$coeff[4,1] - 1.96 * s1model5sum$coeff[4,2]
#  s1model5sum$coeff[4,1] + 1.96 * s1model5sum$coeff[4,2]
#  s1model5sum$coeff[4,3]
#  2*(1-pt(abs(s1model5sum$coeff[4,3]),196))
s1model6sum = summary(lmer(disapp ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model6RSq = r.squaredGLMM(lmer(disapp ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#s1model6sum$coeff[4,1]
#  s1model6sum$coeff[4,1] - 1.96 * s1model6sum$coeff[4,2]
#  s1model6sum$coeff[4,1] + 1.96 * s1model6sum$coeff[4,2]
#  s1model6sum$coeff[4,3]
#  2*(1-pt(abs(s1model6sum$coeff[4,3]),196))
s1model7sum = summary(lmer(surprise ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model7RSq = r.squaredGLMM(lmer(surprise ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#s1model7sum$coeff[4,1]
#  s1model7sum$coeff[4,1] - 1.96 * s1model7sum$coeff[4,2]
#  s1model7sum$coeff[4,1] + 1.96 * s1model7sum$coeff[4,2]
#  s1model7sum$coeff[4,3]
#  2*(1-pt(abs(s1model7sum$coeff[4,3]),196))
s1model8sum = summary(lmer(fear ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model8RSq = r.squaredGLMM(lmer(fear ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
#s1model8sum$coeff[4,1]
#  s1model8sum$coeff[4,1] - 1.96 * s1model8sum$coeff[4,2]
#  s1model8sum$coeff[4,1] + 1.96 * s1model8sum$coeff[4,2]
#  s1model8sum$coeff[4,3]
#  2*(1-pt(abs(s1model8sum$coeff[4,3]),196))



s1model9sum = summary(lmer(positive ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model10sum = summary(lmer(negative ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))

s1model9RSq = r.squaredGLMM(lmer(positive ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))
s1model10RSq = r.squaredGLMM(lmer(negative ~ PE * thirdPerson + (1|workerid) + (1|spinnerID), study1))



```



#### Study 1 Results

Emotion | <u>Simple Effect</u> <br> b [95\% CI] | <br> t | <br> p | <u>Reward Sensitivity (Interaction)</u> <br> b [95\% CI] | <br> t | <br> p | marginal R^2 | conditional R^2
--- | ------- | --- | --- | ------- | --- | --- | --- | ---
Happy | `r format(round(s1model1sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model1sum$coeff[3,1] - 1.96 * s1model1sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model1sum$coeff[3,1] + 1.96 * s1model1sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model1sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model1sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model1sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model1sum$coeff[4,1] - 1.96 * s1model1sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model1sum$coeff[4,1] + 1.96 * s1model1sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model1sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model1sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model1RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model1RSq['R2c'], 3), nsmall=3)`
Content | `r format(round(s1model2sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model2sum$coeff[3,1] - 1.96 * s1model2sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model2sum$coeff[3,1] + 1.96 * s1model2sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model2sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model2sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model2sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model2sum$coeff[4,1] - 1.96 * s1model2sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model2sum$coeff[4,1] + 1.96 * s1model2sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model2sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model2sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model2RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model2RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Positive Composite | `r format(round(s1model9sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model9sum$coeff[3,1] - 1.96 * s1model9sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model9sum$coeff[3,1] + 1.96 * s1model9sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model9sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model9sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model9sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model9sum$coeff[4,1] - 1.96 * s1model9sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model9sum$coeff[4,1] + 1.96 * s1model9sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model9sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model9sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model9RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model9RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; 
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; 
Sad | `r format(round(s1model3sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model3sum$coeff[3,1] - 1.96 * s1model3sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model3sum$coeff[3,1] + 1.96 * s1model3sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model3sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model3sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model3sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model3sum$coeff[4,1] - 1.96 * s1model3sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model3sum$coeff[4,1] + 1.96 * s1model3sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model3sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model3sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model3RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model3RSq['R2c'], 3), nsmall=3)`
Anger | `r format(round(s1model4sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model4sum$coeff[3,1] - 1.96 * s1model4sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model4sum$coeff[3,1] + 1.96 * s1model4sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model4sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model4sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model4sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model4sum$coeff[4,1] - 1.96 * s1model4sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model4sum$coeff[4,1] + 1.96 * s1model4sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model4sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model4sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model4RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model4RSq['R2c'], 3), nsmall=3)`
Disgust | `r format(round(s1model5sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model5sum$coeff[3,1] - 1.96 * s1model5sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model5sum$coeff[3,1] + 1.96 * s1model5sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model5sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model5sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model5sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model5sum$coeff[4,1] - 1.96 * s1model5sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model5sum$coeff[4,1] + 1.96 * s1model5sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model5sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model5sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model5RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model5RSq['R2c'], 3), nsmall=3)`
Disappointment | `r format(round(s1model6sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model6sum$coeff[3,1] - 1.96 * s1model6sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model6sum$coeff[3,1] + 1.96 * s1model6sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model6sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model6sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model6sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model6sum$coeff[4,1] - 1.96 * s1model6sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model6sum$coeff[4,1] + 1.96 * s1model6sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model6sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model6sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model6RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model6RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; 
Negative Composite | `r format(round(s1model10sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model10sum$coeff[3,1] - 1.96 * s1model10sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model10sum$coeff[3,1] + 1.96 * s1model10sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model10sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model10sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model10sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model10sum$coeff[4,1] - 1.96 * s1model10sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model10sum$coeff[4,1] + 1.96 * s1model10sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model10sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model10sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model10RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model10RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; |  &nbsp; | &nbsp; 
Surprise | `r format(round(s1model7sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model7sum$coeff[3,1] - 1.96 * s1model7sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model7sum$coeff[3,1] + 1.96 * s1model7sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model7sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model7sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model7sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model7sum$coeff[4,1] - 1.96 * s1model7sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model7sum$coeff[4,1] + 1.96 * s1model7sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model7sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model7sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model7RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model7RSq['R2c'], 3), nsmall=3)`
Fear | `r format(round(s1model8sum$coeff[3,1], 3), nsmall=3)` [`r format(round(s1model8sum$coeff[3,1] - 1.96 * s1model8sum$coeff[3,2], 3), nsmall=3)`, `r format(round(s1model8sum$coeff[3,1] + 1.96 * s1model8sum$coeff[3,2], 3), nsmall=3)`]  |  `r format(round(s1model8sum$coeff[3,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model8sum$coeff[3,3]),196)), 3), nsmall=3)` | `r format(round(s1model8sum$coeff[4,1], 3), nsmall=3)` [`r format(round(s1model8sum$coeff[4,1] - 1.96 * s1model8sum$coeff[4,2], 3), nsmall=3)`, `r format(round(s1model8sum$coeff[4,1] + 1.96 * s1model8sum$coeff[4,2], 3), nsmall=3)`]  |  `r format(round(s1model8sum$coeff[4,3], 3), nsmall=3)`  |  `r format(round(2*(1-pt(abs(s1model8sum$coeff[4,3]),196)), 3), nsmall=3)` | `r format(round(s1model8RSq['R2m'], 3), nsmall=3)` | `r format(round(s1model8RSq['R2c'], 3), nsmall=3)`

Top: Table 1 in paper. <br>
Study 1 results. Each row indicates the results of one model predicting one emotion (or emotion composite). Left: Coefficients on the simple effect of condition (i.e. the contrast Other-Self at PE=0) in the mixed models. Right: Reward sensitivity, or the coefficient on the Condition*PE interaction term in the mixed models. (n.s. not significant, * p<.05, ** p<.01, *** p<.001) Marginal and Conditional R^2 are reported, after Nakagawa and Schielzeth (2013) 





```{r study1-figures2, fig.height=6, fig.width=8.5, echo=FALSE}
study1DF = data.frame(Contrast = factor(rep(c("Other-Self Simple Effect (at PE=0)", "Condition Interaction with PE"),8),
                                           levels=c("Other-Self Simple Effect (at PE=0)", "Condition Interaction with PE")),
                         Emotion = factor(rep(c("Happy", "Content", "Sad", "Anger", 
                                                "Disgust", "Disappointment", "Surprise", "Fear"),each=2),
                                      levels = c("Happy", "Content", "Sad", "Anger", 
                                                 "Disgust", "Disappointment",
                                                 "Surprise", "Fear")),
                           coef = c(s1model1sum$coefficients[3,1],
                                    s1model1sum$coefficients[4,1],
                                    s1model2sum$coefficients[3,1],
                                    s1model2sum$coefficients[4,1],
                                    s1model3sum$coefficients[3,1],
                                    s1model3sum$coefficients[4,1],
                                    s1model4sum$coefficients[3,1],
                                    s1model4sum$coefficients[4,1],
                                    s1model5sum$coefficients[3,1],
                                    s1model5sum$coefficients[4,1],
                                    s1model6sum$coefficients[3,1],
                                    s1model6sum$coefficients[4,1],
                                    s1model7sum$coefficients[3,1],
                                    s1model7sum$coefficients[4,1],
                                    s1model8sum$coefficients[3,1],
                                    s1model8sum$coefficients[4,1]),
                          se = c(s1model1sum$coefficients[3,2],
                                 s1model1sum$coefficients[4,2],
                                    s1model2sum$coefficients[3,2],
                                    s1model2sum$coefficients[4,2],
                                    s1model3sum$coefficients[3,2],
                                    s1model3sum$coefficients[4,2],
                                    s1model4sum$coefficients[3,2],
                                    s1model4sum$coefficients[4,2],
                                    s1model5sum$coefficients[3,2],
                                    s1model5sum$coefficients[4,2],
                                    s1model6sum$coefficients[3,2],
                                    s1model6sum$coefficients[4,2],
                                    s1model7sum$coefficients[3,2],
                                    s1model7sum$coefficients[4,2],
                                    s1model8sum$coefficients[3,2],
                                    s1model8sum$coefficients[4,2]))

study1DF$ci.h = 1.96 * study1DF$se
study1DF$ci.l = 1.96 * study1DF$se


ggplot(data=study1DF, aes(x=Emotion, y=coef, fill=Emotion)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=coef - ci.l, ymax=coef + ci.h), size=.3, width=.2, position=position_dodge(.9)) +
  scale_fill_brewer(palette="Set1") + facet_wrap(~Contrast, ncol=1, scales="free") +
  theme_bw() + xlab("Emotion") + ylab("Magnitude of Coefficients (b's)") +
  theme(legend.position="none",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
# 8.5 by 6
```

Top (not in paper): Graph of coefficients of individual emotions for Study 1. (Basically a graphical representation of the coefficients in Table 1). Error bars represent 95% CIs.



```{r study1-collapsed-plot, fig.height=4, fig.width=6.5, echo=FALSE}
## For positive and negative only

study1DF_collapsed = data.frame(Emotion = factor(rep(c(rep("Positive",1), rep("Negative",1)),2),
                                          levels = c("Positive", "Negative")),
                           CoeffType = factor(rep(c("Distance simple effect (at PE=0)", "Interaction with PE"),each=2),
                                           levels=c("Distance simple effect (at PE=0)", "Interaction with PE")),
                         Coef = c(s1model9sum$coefficients[3,1],
                                  s1model10sum$coefficients[3,1],
                                  s1model9sum$coefficients[4,1],
                                  s1model10sum$coefficients[4,1]),
                         SE = c(s1model9sum$coefficients[3,2],
                                s1model10sum$coefficients[3,2],
                                s1model9sum$coefficients[4,2],
                                s1model10sum$coefficients[4,2])
                         )
study1DF_collapsed$CI = 1.96*study1DF_collapsed$SE

ggplot(data=study1DF_collapsed, aes(x=Emotion, y=Coef, fill=Emotion)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Coef-CI, ymax=Coef+CI), size=.3, width=.2, position=position_dodge(.9)) + 
  facet_wrap(~CoeffType, ncol=2, scales="free") + 
  #facet_grid(~CoeffType, ncol=1, scales="free") + 
  scale_fill_brewer(palette="Set1") +
  theme_bw() + xlab("Emotion") + ylab("Magnitude of Coefficients (b's)") +
  theme(legend.position="none",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
# pdf 6.5 by 4
```

Top (not in paper): Similar graph, but only for the positive/engative emotion composites. Error bars are 95% CIs.


# Study 2

```{r distance-data-preamble, echo=FALSE, warning=FALSE}
study2.wide <- read.csv('data/study2data.csv', header=T)
for(j in 1:10) {
  # make sure these variables are logical, rather than numeric
  varString = paste("BFItargetSimilarity.", as.character(j), sep="")
  study2.wide[,varString] = as.logical(study2.wide[,varString])
}

# Due to some very bad code writing when I was much more inexperienced (and subsequent use of that legacy code...), the DV names in Study 2 are "q1" through "q8", which, unhelpfully, correspond to:
# "happy", "sad", "anger", "surprise", "disgust", "fear", "content", "disapp"
# in that order. 
# I have sinced changed my scripts to give the DVs more meaningful names, but I did not want to touch the raw data, so unfortunately the variable names are still "q1"-"q8".

# removing those who failed attention check
# "BFI.X" is the participant's response to the Xth question of the BFI-10
# "BFIAttentionCheck.X" is the participant's attention check response ("what did your partner respond?")
# "BFItargetSimilarity.X" is the truth: that is, what the program said that the partner responded.
# Thus,
# BFI.X == BFIAttentionCheck.X   is whether participant gave the same response to himself as to Attention Check
#     and this should be equal to BFItargetSimilarity.X     if participant gave the correct answer.

attentionCheckAnswers = ( ( study2.wide[, c("BFI.1","BFI.2", "BFI.3", "BFI.4", "BFI.5", 
                                             "BFI.6", "BFI.7","BFI.8", "BFI.9", "BFI.10")] 
                             == study2.wide[, c("BFIAttentionCheck.1","BFIAttentionCheck.2", "BFIAttentionCheck.3",
                                                "BFIAttentionCheck.4", "BFIAttentionCheck.5", "BFIAttentionCheck.6",
                                                "BFIAttentionCheck.7","BFIAttentionCheck.8", "BFIAttentionCheck.9",
                                                "BFIAttentionCheck.10")])
                          ==study2.wide[,c("BFItargetSimilarity.1","BFItargetSimilarity.2", "BFItargetSimilarity.3",
                                           "BFItargetSimilarity.4", "BFItargetSimilarity.5", "BFItargetSimilarity.6",
                                           "BFItargetSimilarity.7","BFItargetSimilarity.8", "BFItargetSimilarity.9",
                                           "BFItargetSimilarity.10")] )
study2.wide$use = rowSums(attentionCheckAnswers)==10
# use = 1 only if they answered all 10 attention check questions right.
study2.wide = study2.wide[study2.wide$use==1,] # dropping those who failed attention check


# converting data to long format as in Study 1
study2 <- processData(study2.wide,
                        variableList = c("spinnerID", "payoff1", "payoff2", "payoff3", 
                                         "prob1", "prob2", "prob3",
                                         "winChoice", "win", "winProb",
                                         "angleProp", "reactionTime",
                                         "happy", "sad", "anger", "surprise", 
                                         "disgust", "fear", "content", "disapp"), 
                            idVarList = c("workerid", "gender", "age", "socialDistance", "closeness",
                                          "iOS", "srSimilarity", "srLiking", "srEmpathy"),
                            numTrials = 10)

## below is with BFI included
# study2 <- processData(study2.wide,
#                         variableList = c("spinnerID", "payoff1", "payoff2", "payoff3", 
#                                          "prob1", "prob2", "prob3",
#                                          "winChoice", "win", "winProb",
#                                          "angleProp", "reactionTime",
#                                          "happy", "sad", "anger", "surprise", 
#                                          "disgust", "fear", "content", "disapp"), 
#                             idVarList = c("workerid", "gender", "age", "socialDistance", "closeness",
#                                           "iOS", "srSimilarity", "srLiking", "srEmpathy",
#                                           "BFI.1", "BFI.2", "BFI.3", "BFI.4", "BFI.5", 
#                                           "BFI.6", "BFI.7", "BFI.8", "BFI.9", "BFI.10"),
#                             numTrials = 10)



# Calculating Expected Value and Prediction Error
study2$EV = study2$prob1*study2$payoff1 + study2$prob2*study2$payoff2 + study2$prob3*study2$payoff3
study2$PE = study2$win - study2$EV


study2$socialSimilarity = 10 - study2$socialDistance

# creating emotion composites
study2$positive = (study2$happy + study2$content)/2
study2$negative = (study2$sad + study2$anger + study2$disgust + study2$disapp)/4

```

```{r distance-manip-plots, eval=TRUE, echo=FALSE, message=FALSE, fig.height=8.5, fig.width=8.5}
# Manipulation checks
library(car)
scatterplotMatrix(~socialDistance + iOS + srSimilarity + srLiking + srEmpathy, data=study2.wide)

# cor.test(study2.wide$socialDistance, study2.wide$iOS)
# cor.test(study2.wide$socialDistance, study2.wide$srSimilarity)
# cor.test(study2.wide$socialDistance, study2.wide$srLiking)
# cor.test(study2.wide$socialDistance, study2.wide$srEmpathy)
```

Top (not in paper): correlation plots of the manipulation checks with our manipualted socialDistance variable. iOS: Inclusion of Self in Other Scale. Others: Similarity, Liking, Empathy. See paper for details.

```{r distance-manip-plots2, eval=TRUE, echo=FALSE, message=FALSE, fig.height=4, fig.width=8.5}
study2.wide$sr_iOS = study2.wide$iOS*9/100
study2ManipulationMelt = melt(study2.wide, id=c("workerid", "socialDistance"), 
                                measure = c("sr_iOS", "srSimilarity", "srLiking", "srEmpathy"),
                                variable.name = "ManipulationCheck")
study2ManipulationMelt$ManipulationCheck = factor(study2ManipulationMelt$ManipulationCheck,
                                                    levels = c("sr_iOS", "srSimilarity", "srLiking", "srEmpathy"),
                                                    labels = c("IOS", "Similarity", "Liking", "Empathy"))
ggplot(data=study2ManipulationMelt, aes(x=socialDistance, y=value, color=ManipulationCheck)) + 
  geom_point(size=2, alpha=0.3) + geom_smooth(method=lm, se=FALSE) + 
  scale_y_continuous(limits=c(0,9)) + scale_x_continuous(breaks=c(1, 3, 5, 7, 9)) + 
  theme_bw() + xlab("Social Distance to Target") + ylab("Value of Manipulation Check") +
  theme(strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
```

Top (not in paper): scatterplot of the manipulation checks against our manipualted socialDistance variable.


The manipulation checks confirmed that the psychological distance manipulation had the intended effect on participants’ subjective psychological distance to the target. The manipulated psychological distance was negatively correlated with participants’ ratings on the IOS (r=`r cor(study2.wide$socialDistance, study2.wide$iOS)`; t(236)=`r cor.test(study2.wide$socialDistance, study2.wide$iOS)$statistic`, p<.0001), similarity judgments (r=`r cor(study2.wide$socialDistance, study2.wide$srSimilarity)`; t(236)=`r cor.test(study2.wide$socialDistance, study2.wide$srSimilarity)$statistic`, p<.0001), liking judgments (r=`r cor(study2.wide$socialDistance, study2.wide$srLiking)`; t(236)=`r cor.test(study2.wide$socialDistance, study2.wide$srLiking)$statistic`, p<.0001), and empathy ratings with the target (r=`r cor(study2.wide$socialDistance, study2.wide$srEmpathy)`; t(236)=`r cor.test(study2.wide$socialDistance, study2.wide$srEmpathy)$statistic`, p<.0001).



```{r study2-analysis, echo=FALSE, results='hide'}
socDistanceModel1 <- lmer(happy    ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel2 <- lmer(content  ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel3 <- lmer(sad      ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel4 <- lmer(anger    ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel5 <- lmer(disgust  ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel6 <- lmer(disapp   ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel7 <- lmer(surprise ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel8 <- lmer(fear     ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 

#interaction is row number 4, socDist itself is 3.
s2model1sum=summary(socDistanceModel1)
s2model2sum=summary(socDistanceModel2)
s2model3sum=summary(socDistanceModel3)
s2model4sum=summary(socDistanceModel4)
s2model5sum=summary(socDistanceModel5)
s2model6sum=summary(socDistanceModel6)
s2model7sum=summary(socDistanceModel7)
s2model8sum=summary(socDistanceModel8)


s2model1RSq = r.squaredGLMM(socDistanceModel1)
s2model2RSq = r.squaredGLMM(socDistanceModel2)
s2model3RSq = r.squaredGLMM(socDistanceModel3)
s2model4RSq = r.squaredGLMM(socDistanceModel4)
s2model5RSq = r.squaredGLMM(socDistanceModel5)
s2model6RSq = r.squaredGLMM(socDistanceModel6)
s2model7RSq = r.squaredGLMM(socDistanceModel7)
s2model8RSq = r.squaredGLMM(socDistanceModel8)


socDistanceModel9 <- lmer(positive  ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
socDistanceModel10 <- lmer(negative ~ PE * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 

s2model9sum=summary(socDistanceModel9)
s2model10sum=summary(socDistanceModel10)
s2model9sum$coeff[4,1]
s2model9sum$coeff[4,1] - 1.96 * s2model9sum$coeff[4,2]
s2model9sum$coeff[4,1] + 1.96 * s2model9sum$coeff[4,2]
s2model9sum$coeff[4,3]
2*(1-pt(abs(s2model9sum$coeff[4,3]),232))

s2model10sum$coeff[4,1]
s2model10sum$coeff[4,1] - 1.96 * s2model10sum$coeff[4,2]
s2model10sum$coeff[4,1] + 1.96 * s2model10sum$coeff[4,2]
s2model10sum$coeff[4,3]
2*(1-pt(abs(s2model10sum$coeff[4,3]),232))

s2model9RSq = r.squaredGLMM(socDistanceModel9)
s2model10RSq = r.squaredGLMM(socDistanceModel10)


#study2$openness = 1-1*(study2$BFI.5) + 1*(study2$BFI.10)
#study2$neuroticism = 1-1*(study2$BFI.4) + 1*(study2$BFI.9)
#study2$conscientiousness = 1-1*(study2$BFI.3) + 1*(study2$BFI.8)
#study2$agreeableness = 1-1*(study2$BFI.7) + 1*(study2$BFI.2)
#study2$extraversion = 1-1*(study2$BFI.1) + 1*(study2$BFI.6)

#socDistanceModel9 <- lmer(positive  ~ PE * socialDistance + BFI.9 + (1|workerid) + (1|spinnerID), data = study2); 
#socDistanceModel10 <- lmer(negative ~ PE * socialDistance + BFI.5 + (1|workerid) + (1|spinnerID), data = study2); 

#socDistanceModel9 <- lmer(positive  ~ PE * socialDistance + (agreeableness + extraversion) * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
#socDistanceModel10 <- lmer(negative ~ PE * socialDistance + (agreeableness + extraversion) * socialDistance + (1|workerid) + (1|spinnerID), data = study2); 
#summary(socDistanceModel9)
#summary(socDistanceModel10)


```


#### Study 2 Regression Results

Emotion | <u>Simple Effect</u> <br> b [95\% CI] | <br> t | <br> p | <u>Reward Sensitivity (Interaction)</u> <br> b [95\% CI] | <br> t | <br> p | marginal R^2 | conditional R^2
--- | --- | --- | --- | --- | --- | --- | --- | --- 
Happy | `r format(round(s2model1sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model1sum$coeff[3,1] - 1.96 * s2model1sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model1sum$coeff[3,1] + 1.96 * s2model1sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model1sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model1sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model1sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model1sum$coeff[4,1] - 1.96 * s2model1sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model1sum$coeff[4,1] + 1.96 * s2model1sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model1sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model1sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s2model1RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model1RSq['R2c'], 3), nsmall=3)`
Content | `r format(round(s2model2sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model2sum$coeff[3,1] - 1.96 * s2model2sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model2sum$coeff[3,1] + 1.96 * s2model2sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model2sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model2sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model2sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model2sum$coeff[4,1] - 1.96 * s2model2sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model2sum$coeff[4,1] + 1.96 * s2model2sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model2sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model2sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model2RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model2RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Positive Composite | `r format(round(s2model9sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model9sum$coeff[3,1] - 1.96 * s2model9sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model9sum$coeff[3,1] + 1.96 * s2model9sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model9sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model9sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model9sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model9sum$coeff[4,1] - 1.96 * s2model9sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model9sum$coeff[4,1] + 1.96 * s2model9sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model9sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model9sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model9RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model9RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Sad | `r format(round(s2model3sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model3sum$coeff[3,1] - 1.96 * s2model3sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model3sum$coeff[3,1] + 1.96 * s2model3sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model3sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model3sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model3sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model3sum$coeff[4,1] - 1.96 * s2model3sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model3sum$coeff[4,1] + 1.96 * s2model3sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model3sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model3sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model3RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model3RSq['R2c'], 3), nsmall=3)`
Anger | `r format(round(s2model4sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model4sum$coeff[3,1] - 1.96 * s2model4sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model4sum$coeff[3,1] + 1.96 * s2model4sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model4sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model4sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model4sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model4sum$coeff[4,1] - 1.96 * s2model4sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model4sum$coeff[4,1] + 1.96 * s2model4sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model4sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model4sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model4RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model4RSq['R2c'], 3), nsmall=3)`
Disgust | `r format(round(s2model5sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model5sum$coeff[3,1] - 1.96 * s2model5sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model5sum$coeff[3,1] + 1.96 * s2model5sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model5sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model5sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model5sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model5sum$coeff[4,1] - 1.96 * s2model5sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model5sum$coeff[4,1] + 1.96 * s2model5sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model5sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model5sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model5RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model5RSq['R2c'], 3), nsmall=3)`
Disappointment | `r format(round(s2model6sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model6sum$coeff[3,1] - 1.96 * s2model6sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model6sum$coeff[3,1] + 1.96 * s2model6sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model6sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model6sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model6sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model6sum$coeff[4,1] - 1.96 * s2model6sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model6sum$coeff[4,1] + 1.96 * s2model6sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model6sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model6sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model6RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model6RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Negative Composite | `r format(round(s2model10sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model10sum$coeff[3,1] - 1.96 * s2model10sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model10sum$coeff[3,1] + 1.96 * s2model10sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model10sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model10sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model10sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model10sum$coeff[4,1] - 1.96 * s2model10sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model10sum$coeff[4,1] + 1.96 * s2model10sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model10sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model10sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model10RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model10RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Surprise | `r format(round(s2model7sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model7sum$coeff[3,1] - 1.96 * s2model7sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model7sum$coeff[3,1] + 1.96 * s2model7sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model7sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model7sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model7sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model7sum$coeff[4,1] - 1.96 * s2model7sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model7sum$coeff[4,1] + 1.96 * s2model7sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model7sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model7sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model7RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model7RSq['R2c'], 3), nsmall=3)`
Fear | `r format(round(s2model8sum$coeff[3,1], 3), digits=3)` [`r format(round(s2model8sum$coeff[3,1] - 1.96 * s2model8sum$coeff[3,2], 3), digits=3)`, `r format(round(s2model8sum$coeff[3,1] + 1.96 * s2model8sum$coeff[3,2], 3), digits=3)`] | `r format(round(s2model8sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model8sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s2model8sum$coeff[4,1], 3), digits=3)` [`r format(round(s2model8sum$coeff[4,1] - 1.96 * s2model8sum$coeff[4,2], 3), digits=3)`, `r format(round(s2model8sum$coeff[4,1] + 1.96 * s2model8sum$coeff[4,2], 3), digits=3)`] | `r format(round(s2model8sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s2model8sum$coeff[4,3]),196)), 3), digits=3)`  | `r format(round(s2model8RSq['R2m'], 3), nsmall=3)` | `r format(round(s2model8RSq['R2c'], 3), nsmall=3)`



```{r study2-plot-all-emotions, fig.height=5, fig.width=8.5, echo=FALSE}
## for all emotions
study2DF = data.frame(Emotion = factor(rep(c(rep("Happy",1), rep("Content",1), rep("Sad",1), rep("Anger",1),
                                            rep("Disgust",1), rep("Disappointment",1), 
                                            rep("Surprise",1), rep("Fear",1)),2),
                                          levels = c("Happy", "Content",
                                                     "Sad", "Anger",  
                                                     "Disgust", "Disappointment", 
                                                     "Surprise", "Fear")),
                           CoeffType = factor(rep(c("Distance Interaction with PE", "Distance simple effect (at PE=0)"),each=8),
                                           levels=c("Distance simple effect (at PE=0)", "Distance Interaction with PE")),
                         Coef = c(summary(socDistanceModel1)$coefficients[4,1],
                                  summary(socDistanceModel2)$coefficients[4,1],
                                  summary(socDistanceModel3)$coefficients[4,1],
                                  summary(socDistanceModel4)$coefficients[4,1],
                                  summary(socDistanceModel5)$coefficients[4,1],
                                  summary(socDistanceModel6)$coefficients[4,1],
                                  summary(socDistanceModel7)$coefficients[4,1],
                                  summary(socDistanceModel8)$coefficients[4,1],
                                  summary(socDistanceModel1)$coefficients[3,1],
                                  summary(socDistanceModel2)$coefficients[3,1],
                                  summary(socDistanceModel3)$coefficients[3,1],
                                  summary(socDistanceModel4)$coefficients[3,1],
                                  summary(socDistanceModel5)$coefficients[3,1],
                                  summary(socDistanceModel6)$coefficients[3,1],
                                  summary(socDistanceModel7)$coefficients[3,1],
                                  summary(socDistanceModel8)$coefficients[3,1]),
                         SE = c(summary(socDistanceModel1)$coefficients[4,2],
                                summary(socDistanceModel2)$coefficients[4,2],
                                summary(socDistanceModel3)$coefficients[4,2],
                                summary(socDistanceModel4)$coefficients[4,2],
                                summary(socDistanceModel5)$coefficients[4,2],
                                summary(socDistanceModel6)$coefficients[4,2],
                                summary(socDistanceModel7)$coefficients[4,2],
                                summary(socDistanceModel8)$coefficients[4,2],
                                summary(socDistanceModel1)$coefficients[3,2],
                                summary(socDistanceModel2)$coefficients[3,2],
                                summary(socDistanceModel3)$coefficients[3,2],
                                summary(socDistanceModel4)$coefficients[3,2],
                                summary(socDistanceModel5)$coefficients[3,2],
                                summary(socDistanceModel6)$coefficients[3,2],
                                summary(socDistanceModel7)$coefficients[3,2],
                                summary(socDistanceModel8)$coefficients[3,2])
                         )
study2DF$CI = 1.96*study2DF$SE

ggplot(data=study2DF, aes(x=Emotion, y=Coef, fill=Emotion)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Coef-CI, ymax=Coef+CI), size=.3, width=.2, position=position_dodge(.9)) + facet_wrap(~CoeffType, ncol=1, scales="free") + scale_fill_brewer(palette="Set1") +
  theme_bw() + xlab("Emotion") + ylab("Magnitude of Coefficients (b's)") +
  theme(legend.position="none",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
# pdf 8.5 by 6

```

Top (not in paper): Graph of coefficients of individual emotions for Study 2. Error bars represent 95% CIs.


```{r study2-plot, fig.height=4, fig.width=6.5, echo=FALSE}
## For positive and negative only
study2DF_collapsed = data.frame(Emotion = factor(rep(c(rep("Positive",1), rep("Negative",1)),2),
                                          levels = c("Positive", "Negative")),
                           CoeffType = factor(rep(c("Distance simple effect (at PE=0)", "Interaction with PE"),each=2),
                                           levels=c("Distance simple effect (at PE=0)", "Interaction with PE")),
                         Coef = c(summary(socDistanceModel9)$coefficients[3,1],
                                  summary(socDistanceModel10)$coefficients[3,1],
                                  summary(socDistanceModel9)$coefficients[4,1],
                                  summary(socDistanceModel10)$coefficients[4,1]),
                         SE = c(summary(socDistanceModel9)$coefficients[3,2],
                                summary(socDistanceModel10)$coefficients[3,2],
                                summary(socDistanceModel9)$coefficients[4,2],
                                summary(socDistanceModel10)$coefficients[4,2])
                         )
study2DF_collapsed$CI = 1.96*study2DF_collapsed$SE

study2DF_collapsed$CoeffTypeRenamed = factor(study2DF_collapsed$CoeffType,
                                             levels=c("Distance simple effect (at PE=0)",
                                                      "Interaction with PE"),
                                             labels=c("Distance simple effect (at PE=0)",
                                                      "Reward Sensitivity x Distance"))
ggplot(data=study2DF_collapsed, aes(x=Emotion, y=Coef, fill=Emotion)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Coef-CI, ymax=Coef+CI), size=.3, width=.2, position=position_dodge(.9)) + 
  facet_wrap(~CoeffTypeRenamed, ncol=2, scales="free") + 
  #facet_grid(~CoeffType, ncol=1, scales="free") + 
  scale_fill_brewer(palette="Set2") +
  theme_bw() + xlab("Composite Emotions") + ylab("Magnitude of Coefficients (b's)") +
  theme(legend.position="none",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
# pdf 6.5 by 4
```

Top (Figure 4 in paper): <br>
Study 2 results: Left: Simple effect (i.e., the effect of social distance at PE=0). Right: Reward sensitivity across social distance (i.e., interaction of social distance with PE). Error bars represent 95% Confidence Intervals. 



# Study 3

```{r wheelTime-data-preamble, echo=FALSE}
study3 <- read.csv('data/study3data.csv', header=T)
# study 3 has already been preprocessed into long form data, because there were several different datasets lying around and I wanted to combine them into one file.

# this is a 2x2 between-participant design {self/other} x {now/future}.
# firstPerson = 1 if participants were in the "self" condition, and 0 if they were in the "other" condition
#    thirdPerson = 1 - firstPerson
# retrospective = 1 if participants were in the "now" condition, and 0 if they were in the "future" condition
#    prospective = 1 - retrospective

# other variables are the same as Studies 1/2

# calculating EV and PE
study3$EV = study3$prob1*study3$payoff1 + study3$prob2*study3$payoff2 + study3$prob3*study3$payoff3
study3$PE = study3$win - study3$EV

# creating composites
study3$positive = (study3$happy + study3$content)/2
study3$negative = (study3$sad + study3$anger + study3$disgust + study3$disapp)/4
```



```{r study3-analysis, echo=FALSE, results='hide'}
# want "self-now" to be the base condition, so use "thirdPerson" and "prospective" as the dummy variables.
s3model1 = lmer(happy    ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model2 = lmer(content  ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model3 = lmer(sad      ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model4 = lmer(anger    ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model5 = lmer(disgust  ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model6 = lmer(disapp   ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model7 = lmer(surprise ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model8 = lmer(fear     ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)

s3model9 = lmer(positive     ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)
s3model10 = lmer(negative     ~ PE*thirdPerson*prospective + (1|workerid) + (1|spinnerID), data = study3)

  
s3model1sum = summary(s3model1)
s3model2sum = summary(s3model2)
s3model3sum = summary(s3model3)
s3model4sum = summary(s3model4)
s3model5sum = summary(s3model5)
s3model6sum = summary(s3model6)
s3model7sum = summary(s3model7)
s3model8sum = summary(s3model8)

s3model9sum = summary(s3model9) 
s3model10sum = summary(s3model10) 

s3model1RSq = r.squaredGLMM(s3model1)
s3model2RSq = r.squaredGLMM(s3model2)
s3model3RSq = r.squaredGLMM(s3model3)
s3model4RSq = r.squaredGLMM(s3model4)
s3model5RSq = r.squaredGLMM(s3model5)
s3model6RSq = r.squaredGLMM(s3model6)
s3model7RSq = r.squaredGLMM(s3model7)
s3model8RSq = r.squaredGLMM(s3model8)

s3model9RSq = r.squaredGLMM(s3model9)
s3model10RSq = r.squaredGLMM(s3model10)


# currentValue = 5
# s3model9sum$coefficients[currentValue,1]
# s3model9sum$coefficients[currentValue,1] - 1.96 * s3model9sum$coefficients[currentValue,2]
# s3model9sum$coefficients[currentValue,1] + 1.96 * s3model9sum$coefficients[currentValue,2]
# s3model9sum$coefficients[currentValue,3]
# 2*(1-pt(abs(s3model9sum$coefficients[currentValue,3]),378))
# 
# #currentValue = 4
# s3model10sum$coefficients[currentValue,1]
# s3model10sum$coefficients[currentValue,1] - 1.96 * s3model10sum$coefficients[currentValue,2]
# s3model10sum$coefficients[currentValue,1] + 1.96 * s3model10sum$coefficients[currentValue,2]
# s3model10sum$coefficients[currentValue,3]
# 2*(1-pt(abs(s3model10sum$coefficients[currentValue,3]),378))
```


```{r study3-coeff-plot-2, echo=FALSE, fig.height=5, fig.width=8.5}
study3PlotDF = data.frame(Emotion = factor(rep(c(rep("Happy",1), rep("Content",1), rep("Sad",1), rep("Anger",1),
                                            rep("Disgust",1), rep("Disappointment",1), 
                                            rep("Surprise",1), rep("Fear",1)), 4),
                                          levels = c("Happy", "Content",
                                                     "Sad", "Anger",  
                                                     "Disgust", "Disappointment", 
                                                     "Surprise", "Fear")),
                          Contrast = factor( rep(c(rep("Other-Self ", 8), rep("Future-Now", 8)), 2),
                                             levels=c("Other-Self ", "Future-Now")),
                          CoeffType = factor(rep(c("Condition Interaction with PE", 
                                                   "Condition simple effect (at PE=0)"),each=16),
                                           levels=c("Condition simple effect (at PE=0)", 
                                                    "Condition Interaction with PE")),
                         Coef = c(s3model1sum$coefficients[5,1],
                                  s3model2sum$coefficients[5,1],
                                  s3model3sum$coefficients[5,1],
                                  s3model4sum$coefficients[5,1],
                                  s3model5sum$coefficients[5,1],
                                  s3model6sum$coefficients[5,1],
                                  s3model7sum$coefficients[5,1],
                                  s3model8sum$coefficients[5,1],
                                  s3model1sum$coefficients[6,1],
                                  s3model2sum$coefficients[6,1],
                                  s3model3sum$coefficients[6,1],
                                  s3model4sum$coefficients[6,1],
                                  s3model5sum$coefficients[6,1],
                                  s3model6sum$coefficients[6,1],
                                  s3model7sum$coefficients[6,1],
                                  s3model8sum$coefficients[6,1],
                                  s3model1sum$coefficients[3,1],
                                  s3model2sum$coefficients[3,1],
                                  s3model3sum$coefficients[3,1],
                                  s3model4sum$coefficients[3,1],
                                  s3model5sum$coefficients[3,1],
                                  s3model6sum$coefficients[3,1],
                                  s3model7sum$coefficients[3,1],
                                  s3model8sum$coefficients[3,1],
                                  s3model1sum$coefficients[4,1],
                                  s3model2sum$coefficients[4,1],
                                  s3model3sum$coefficients[4,1],
                                  s3model4sum$coefficients[4,1],
                                  s3model5sum$coefficients[4,1],
                                  s3model6sum$coefficients[4,1],
                                  s3model7sum$coefficients[4,1],
                                  s3model8sum$coefficients[4,1]),
                         SE = c(s3model1sum$coefficients[5,2],
                                s3model2sum$coefficients[5,2],
                                s3model3sum$coefficients[5,2],
                                s3model4sum$coefficients[5,2],
                                s3model5sum$coefficients[5,2],
                                s3model6sum$coefficients[5,2],
                                s3model7sum$coefficients[5,2],
                                s3model8sum$coefficients[5,2],
                                s3model1sum$coefficients[6,2],
                                s3model2sum$coefficients[6,2],
                                s3model3sum$coefficients[6,2],
                                s3model4sum$coefficients[6,2],
                                s3model5sum$coefficients[6,2],
                                s3model6sum$coefficients[6,2],
                                s3model7sum$coefficients[6,2],
                                s3model8sum$coefficients[6,2],
                                s3model1sum$coefficients[3,2],
                                s3model2sum$coefficients[3,2],
                                s3model3sum$coefficients[3,2],
                                s3model4sum$coefficients[3,2],
                                s3model5sum$coefficients[3,2],
                                s3model6sum$coefficients[3,2],
                                s3model7sum$coefficients[3,2],
                                s3model8sum$coefficients[3,2],
                                s3model1sum$coefficients[4,2],
                                s3model2sum$coefficients[4,2],
                                s3model3sum$coefficients[4,2],
                                s3model4sum$coefficients[4,2],
                                s3model5sum$coefficients[4,2],
                                s3model6sum$coefficients[4,2],
                                s3model7sum$coefficients[4,2],
                                s3model8sum$coefficients[4,2])
                         )

study3PlotDF$CI = 1.96*study3PlotDF$SE

ggplot(data=study3PlotDF, aes(x=Emotion, y=Coef, fill=Contrast)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Coef-CI, ymax=Coef+CI), size=.3, width=.2, position=position_dodge(.9)) +
  #scale_fill_brewer(palette="Set3")
  scale_fill_manual(values=cbbwPal2) + facet_wrap(~CoeffType, ncol=1, scales="free") +
  theme_bw() + xlab("Emotion") + ylab("Magnitude of Coefficients (b's)") +
  theme(legend.position="top",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
# 8.5 x 5

```

Top (not in paper): Graph of coefficients of individual emotions for Study 3. Error bars represent 95% CIs.


```{r study3-coeff-plot, echo=FALSE, fig.height=4, fig.width=6.5}
## for positive / negative only

study3PlotDF_collapsed = data.frame(Emotion = factor(rep(c(rep("Positive",1), rep("Negative",1)), 4),
                                          levels = c("Positive", "Negative")),
                          Contrast = factor( rep(c(rep("Self-Other ", 2), rep("Now-Future", 2)), 2),
                                             levels=c("Self-Other ", "Now-Future")),
                          CoeffType = factor(rep(c("Condition Interaction with PE", 
                                                   "Condition simple effect (at PE=0)"), each=4),
                                           levels=c("Condition simple effect (at PE=0)", 
                                                    "Condition Interaction with PE")),
                         Coef = c(s3model9sum$coefficients[5,1],
                                  s3model10sum$coefficients[5,1],
                                  s3model9sum$coefficients[6,1],
                                  s3model10sum$coefficients[6,1],
                                  s3model9sum$coefficients[3,1],
                                  s3model10sum$coefficients[3,1],
                                  s3model9sum$coefficients[4,1],
                                  s3model10sum$coefficients[4,1]),
                         SE = c(s3model9sum$coefficients[5,2],
                                s3model10sum$coefficients[5,2],
                                s3model9sum$coefficients[6,2],
                                s3model10sum$coefficients[6,2],
                                s3model9sum$coefficients[3,2],
                                s3model10sum$coefficients[3,2],
                                s3model9sum$coefficients[4,2],
                                s3model10sum$coefficients[4,2])
                         )
study3PlotDF_collapsed$CI = 1.96*study3PlotDF_collapsed$SE


study3PlotDF_collapsed$CoeffTypeRenamed = factor(study3PlotDF_collapsed$CoeffType,
                                             levels=c("Condition simple effect (at PE=0)",
                                                      "Condition Interaction with PE"),
                                             labels=c("Distance simple effect (at PE=0)",
                                                      "Reward Sensitivity x Distance"))

ggplot(data=study3PlotDF_collapsed, aes(x=Emotion, y=Coef, fill=Contrast)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Coef-CI, ymax=Coef+CI), size=.3, width=.2, position=position_dodge(.9)) +
  #scale_fill_brewer(palette="Set3") 
  scale_fill_manual(values=cbbwPal2)+ facet_wrap(~CoeffTypeRenamed, ncol=2, scales="free") +
  theme_bw() + xlab("Composite Emotions") + ylab("Magnitude of Coefficients (b's)") +
  theme(legend.position="top",
        strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.8),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
#6.5 x 4
```


Top (Figure 5 in paper): <br>
Study 3 results: Left: Simple effect by distance (i.e., the effect of the distance manipulations at PE=0). Right: Reward sensitivity across psychological distance (i.e., the interactions of the two distance manipulations with PE). Error bars represent 95% Confidence Intervals. 








Emotion | <u>Three way interaction</u> <br> b [95\% CI] | <br> t | <br> p | marginal R^2 | conditional R^2
--- | --- | --- | --- | --- | ---
Happy | `r format(round(s3model1sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model1sum$coeff[8,1] - 1.96 * s3model1sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model1sum$coeff[8,1] + 1.96 * s3model1sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model1sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model1sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model1RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model1RSq['R2c'], 3), nsmall=3)`
Content | `r format(round(s3model2sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model2sum$coeff[8,1] - 1.96 * s3model2sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model2sum$coeff[8,1] + 1.96 * s3model2sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model2sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model2sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model2RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model2RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Positive Composite | `r format(round(s3model9sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model9sum$coeff[8,1] - 1.96 * s3model9sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model9sum$coeff[8,1] + 1.96 * s3model9sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model9sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model9sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model9RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model9RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Sad | `r format(round(s3model3sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model3sum$coeff[8,1] - 1.96 * s3model3sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model3sum$coeff[8,1] + 1.96 * s3model3sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model3sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model3sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model3RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model3RSq['R2c'], 3), nsmall=3)`
Anger | `r format(round(s3model4sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model4sum$coeff[8,1] - 1.96 * s3model4sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model4sum$coeff[8,1] + 1.96 * s3model4sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model4sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model4sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model4RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model4RSq['R2c'], 3), nsmall=3)`
Disgust | `r format(round(s3model5sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model5sum$coeff[8,1] - 1.96 * s3model5sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model5sum$coeff[8,1] + 1.96 * s3model5sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model5sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model5sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model5RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model5RSq['R2c'], 3), nsmall=3)`
Disappointment | `r format(round(s3model6sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model6sum$coeff[8,1] - 1.96 * s3model6sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model6sum$coeff[8,1] + 1.96 * s3model6sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model6sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model6sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model6RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model6RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Negative Composite | `r format(round(s3model10sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model10sum$coeff[8,1] - 1.96 * s3model10sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model10sum$coeff[8,1] + 1.96 * s3model10sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model10sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model10sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model10RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model10RSq['R2c'], 3), nsmall=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Surprise | `r format(round(s3model7sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model7sum$coeff[8,1] - 1.96 * s3model7sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model7sum$coeff[8,1] + 1.96 * s3model7sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model7sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model7sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model7RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model7RSq['R2c'], 3), nsmall=3)`
Fear | `r format(round(s3model8sum$coeff[8,1], 3), digits=3)` [`r format(round(s3model8sum$coeff[8,1] - 1.96 * s3model8sum$coeff[8,2], 3), digits=3)`, `r format(round(s3model8sum$coeff[8,1] + 1.96 * s3model8sum$coeff[8,2], 3), digits=3)`] | `r format(round(s3model8sum$coeff[8,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model8sum$coeff[8,3]),196)), 3), digits=3)` | `r format(round(s3model8RSq['R2m'], 3), nsmall=3)` | `r format(round(s3model8RSq['R2c'], 3), nsmall=3)`

Top (not in paper): Additional Data on 3 way (PE x social x temporal) interaction in Study 3.

## Supplemental Materials


Emotion | <u>Simple Effect of SOCIAL DISTANCE</u> <br> b [95\% CI] | <br> t | <br> p | <u>Reward Sensitivity (Interaction)  of SOCIAL DISTANCE</u> <br> b [95\% CI] | <br> t | <br> p | <u>Simple Effect of TEMPORAL DISTANCE</u> <br> b [95\% CI] | <br> t | <br> p | <u>Reward Sensitivity (Interaction)  of TEMPORAL DISTANCE</u> <br> b [95\% CI] | <br> t | <br> p
--- | --- | --- | --- | --- | --- | --- | --- | --- | --- | --- | --- | ---
Happy | `r format(round(s3model1sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model1sum$coeff[3,1] - 1.96 * s3model1sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model1sum$coeff[3,1] + 1.96 * s3model1sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model1sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model1sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model1sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model1sum$coeff[5,1] - 1.96 * s3model1sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model1sum$coeff[5,1] + 1.96 * s3model1sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model1sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model1sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model1sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model1sum$coeff[4,1] - 1.96 * s3model1sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model1sum$coeff[4,1] + 1.96 * s3model1sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model1sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model1sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model1sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model1sum$coeff[6,1] - 1.96 * s3model1sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model1sum$coeff[6,1] + 1.96 * s3model1sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model1sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model1sum$coeff[6,3]),196)), 3), digits=3)`
Content | `r format(round(s3model2sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model2sum$coeff[3,1] - 1.96 * s3model2sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model2sum$coeff[3,1] + 1.96 * s3model2sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model2sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model2sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model2sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model2sum$coeff[5,1] - 1.96 * s3model2sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model2sum$coeff[5,1] + 1.96 * s3model2sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model2sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model2sum$coeff[5,3]),196)), 3), digits=3)`  | `r format(round(s3model2sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model2sum$coeff[4,1] - 1.96 * s3model2sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model2sum$coeff[4,1] + 1.96 * s3model2sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model2sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model2sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model2sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model2sum$coeff[6,1] - 1.96 * s3model2sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model2sum$coeff[6,1] + 1.96 * s3model2sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model2sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model2sum$coeff[6,3]),196)), 3), digits=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Positive Composite | `r format(round(s3model9sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model9sum$coeff[3,1] - 1.96 * s3model9sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model9sum$coeff[3,1] + 1.96 * s3model9sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model9sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model9sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model9sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model9sum$coeff[5,1] - 1.96 * s3model9sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model9sum$coeff[5,1] + 1.96 * s3model9sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model9sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model9sum$coeff[5,3]),196)), 3), digits=3)`  | `r format(round(s3model9sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model9sum$coeff[4,1] - 1.96 * s3model9sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model9sum$coeff[4,1] + 1.96 * s3model9sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model9sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model9sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model9sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model9sum$coeff[6,1] - 1.96 * s3model9sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model9sum$coeff[6,1] + 1.96 * s3model9sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model9sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model9sum$coeff[6,3]),196)), 3), digits=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Sad | `r format(round(s3model3sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model3sum$coeff[3,1] - 1.96 * s3model3sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model3sum$coeff[3,1] + 1.96 * s3model3sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model3sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model3sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model3sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model3sum$coeff[5,1] - 1.96 * s3model3sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model3sum$coeff[5,1] + 1.96 * s3model3sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model3sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model3sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model3sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model3sum$coeff[4,1] - 1.96 * s3model3sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model3sum$coeff[4,1] + 1.96 * s3model3sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model3sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model3sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model3sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model3sum$coeff[6,1] - 1.96 * s3model3sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model3sum$coeff[6,1] + 1.96 * s3model3sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model3sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model3sum$coeff[6,3]),196)), 3), digits=3)`
Anger | `r format(round(s3model4sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model4sum$coeff[3,1] - 1.96 * s3model4sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model4sum$coeff[3,1] + 1.96 * s3model4sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model4sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model4sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model4sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model4sum$coeff[5,1] - 1.96 * s3model4sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model4sum$coeff[5,1] + 1.96 * s3model4sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model4sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model4sum$coeff[5,3]),196)), 3), digits=3)`  | `r format(round(s3model4sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model4sum$coeff[4,1] - 1.96 * s3model4sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model4sum$coeff[4,1] + 1.96 * s3model4sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model4sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model4sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model4sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model4sum$coeff[6,1] - 1.96 * s3model4sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model4sum$coeff[6,1] + 1.96 * s3model4sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model4sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model4sum$coeff[6,3]),196)), 3), digits=3)`
Disgust | `r format(round(s3model5sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model5sum$coeff[3,1] - 1.96 * s3model5sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model5sum$coeff[3,1] + 1.96 * s3model5sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model5sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model5sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model5sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model5sum$coeff[5,1] - 1.96 * s3model5sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model5sum$coeff[5,1] + 1.96 * s3model5sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model5sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model5sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model5sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model5sum$coeff[4,1] - 1.96 * s3model5sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model5sum$coeff[4,1] + 1.96 * s3model5sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model5sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model5sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model5sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model5sum$coeff[6,1] - 1.96 * s3model5sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model5sum$coeff[6,1] + 1.96 * s3model5sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model5sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model5sum$coeff[6,3]),196)), 3), digits=3)`
Disappointment | `r format(round(s3model6sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model6sum$coeff[3,1] - 1.96 * s3model6sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model6sum$coeff[3,1] + 1.96 * s3model6sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model6sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model6sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model6sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model6sum$coeff[5,1] - 1.96 * s3model6sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model6sum$coeff[5,1] + 1.96 * s3model6sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model6sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model6sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model6sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model6sum$coeff[4,1] - 1.96 * s3model6sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model6sum$coeff[4,1] + 1.96 * s3model6sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model6sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model6sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model6sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model6sum$coeff[6,1] - 1.96 * s3model6sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model6sum$coeff[6,1] + 1.96 * s3model6sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model6sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model6sum$coeff[6,3]),196)), 3), digits=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Negative Composite | `r format(round(s3model10sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model10sum$coeff[3,1] - 1.96 * s3model10sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model10sum$coeff[3,1] + 1.96 * s3model10sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model10sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model10sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model10sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model10sum$coeff[5,1] - 1.96 * s3model10sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model10sum$coeff[5,1] + 1.96 * s3model10sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model10sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model10sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model10sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model10sum$coeff[4,1] - 1.96 * s3model10sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model10sum$coeff[4,1] + 1.96 * s3model10sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model10sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model10sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model10sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model10sum$coeff[6,1] - 1.96 * s3model10sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model10sum$coeff[6,1] + 1.96 * s3model10sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model10sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model10sum$coeff[6,3]),196)), 3), digits=3)`
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
&nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp; | &nbsp;
Surprise | `r format(round(s3model7sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model7sum$coeff[3,1] - 1.96 * s3model7sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model7sum$coeff[3,1] + 1.96 * s3model7sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model7sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model7sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model7sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model7sum$coeff[5,1] - 1.96 * s3model7sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model7sum$coeff[5,1] + 1.96 * s3model7sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model7sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model7sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model7sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model7sum$coeff[4,1] - 1.96 * s3model7sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model7sum$coeff[4,1] + 1.96 * s3model7sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model7sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model7sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model7sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model7sum$coeff[6,1] - 1.96 * s3model7sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model7sum$coeff[6,1] + 1.96 * s3model7sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model7sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model7sum$coeff[6,3]),196)), 3), digits=3)`
Fear | `r format(round(s3model8sum$coeff[3,1], 3), digits=3)` [`r format(round(s3model8sum$coeff[3,1] - 1.96 * s3model8sum$coeff[3,2], 3), digits=3)`, `r format(round(s3model8sum$coeff[3,1] + 1.96 * s3model8sum$coeff[3,2], 3), digits=3)`] | `r format(round(s3model8sum$coeff[3,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model8sum$coeff[3,3]),196)), 3), digits=3)` | `r format(round(s3model8sum$coeff[5,1], 3), digits=3)` [`r format(round(s3model8sum$coeff[5,1] - 1.96 * s3model8sum$coeff[5,2], 3), digits=3)`, `r format(round(s3model8sum$coeff[5,1] + 1.96 * s3model8sum$coeff[5,2], 3), digits=3)`] | `r format(round(s3model8sum$coeff[5,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model8sum$coeff[5,3]),196)), 3), digits=3)` | `r format(round(s3model8sum$coeff[4,1], 3), digits=3)` [`r format(round(s3model8sum$coeff[4,1] - 1.96 * s3model8sum$coeff[4,2], 3), digits=3)`, `r format(round(s3model8sum$coeff[4,1] + 1.96 * s3model8sum$coeff[4,2], 3), digits=3)`] | `r format(round(s3model8sum$coeff[4,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model8sum$coeff[4,3]),196)), 3), digits=3)` | `r format(round(s3model8sum$coeff[6,1], 3), digits=3)` [`r format(round(s3model8sum$coeff[6,1] - 1.96 * s3model8sum$coeff[6,2], 3), digits=3)`, `r format(round(s3model8sum$coeff[6,1] + 1.96 * s3model8sum$coeff[6,2], 3), digits=3)`] | `r format(round(s3model8sum$coeff[6,3], 3), digits=3)` | `r format(round(2*(1-pt(abs(s3model8sum$coeff[6,3]),196)), 3), digits=3)`

Top: Table S1 in the Supplemental Materials. Table of regression coefficients, with p-values in parentheses. We have presented the table to facilitate comparison across studies and emotions: The top half of the table contains the coefficients for the simple effect of distance (at PE=0). The bottom half of the table contains the coefficients for reward sensitivity across psychological distance (interaction of distance with PE). The contrasts are always in a direction taking the Self (Now) as a reference point; hence the coefficients should be interpreted as the effect of increasing distance. The three-way interactions for Study 3 are omitted for clarity. (\* p<.05, \*\* p<.01, \*\*\* p<.001)




```{r old-table, eval=FALSE, echo=FALSE}
# This contains the code that I used for a PREVIOUS, older version of the tables.

## Three Way Interactions
##### Interactions
Happy (b=`r s3model1sum$coeff[8,1]` [`r s3model1sum$coeff[8,1] - 1.96 * s3model1sum$coeff[8,2]`, `r s3model1sum$coeff[8,1] + 1.96 * s3model1sum$coeff[8,2]`], t(390)=`r s3model1sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model1sum$coeff[8,3]),390))`)

Content (b=`r s3model2sum$coeff[8,1]` [`r s3model2sum$coeff[8,1] - 1.96 * s3model2sum$coeff[8,2]`, `r  s3model2sum$coeff[8,1] + 1.96 * s3model2sum$coeff[8,2]`], t(390)=`r s3model2sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model2sum$coeff[8,3]),390))`)

Sad (b=`r s3model3sum$coeff[8,1]` [`r s3model3sum$coeff[8,1] - 1.96 * s3model3sum$coeff[8,2]`, `r s3model3sum$coeff[8,1] + 1.96 * s3model3sum$coeff[8,2]`], t(390)=`r s3model3sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model3sum$coeff[8,3]),390))`)

Anger (b=`r s3model4sum$coeff[8,1]` [`r s3model4sum$coeff[8,1] - 1.96 * s3model4sum$coeff[8,2]`, `r s3model4sum$coeff[8,1] + 1.96 * s3model4sum$coeff[8,2]`], t(390)=`r s3model4sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model4sum$coeff[8,3]),390))`)

Disgust (b=`r s3model5sum$coeff[8,1]` [`r s3model5sum$coeff[8,1] - 1.96 * s3model5sum$coeff[8,2]`, `r s3model5sum$coeff[8,1] + 1.96 * s3model5sum$coeff[8,2]`], t(390)=`r s3model5sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model5sum$coeff[8,3]),390))`)

Disappointment (b=`r s3model6sum$coeff[8,1]` [`r s3model6sum$coeff[8,1] - 1.96 * s3model6sum$coeff[8,2]`, `r s3model6sum$coeff[8,1] + 1.96 * s3model6sum$coeff[8,2]`], t(390)=`r s3model6sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model6sum$coeff[8,3]),390))`)

Surprise (b=`r s3model7sum$coeff[8,1]` [`r s3model7sum$coeff[8,1] - 1.96 * s3model7sum$coeff[8,2]`, `r s3model7sum$coeff[8,1] + 1.96 * s3model7sum$coeff[8,2]`], t(390)=`r s3model7sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model7sum$coeff[8,3]),390))`)

Fear (b=`r s3model8sum$coeff[8,1]` [`r s3model8sum$coeff[8,1] - 1.96 * s3model8sum$coeff[8,2]`, `r s3model8sum$coeff[8,1] + 1.96 * s3model8sum$coeff[8,2]`], t(390)=`r s3model8sum$coeff[8,3]` , p=`r 2*(1-pt(abs(s3model8sum$coeff[8,3]),390))`)


## With Third Person
##### Interactions
Happy (b=`r s3model1sum$coeff[5,1]` [`r s3model1sum$coeff[5,1] - 1.96 * s3model1sum$coeff[5,2]`, `r s3model1sum$coeff[5,1] + 1.96 * s3model1sum$coeff[5,2]`], t(390)=`r s3model1sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model1sum$coeff[5,3]),390))`)

Content (b=`r s3model2sum$coeff[5,1]` [`r s3model2sum$coeff[5,1] - 1.96 * s3model2sum$coeff[5,2]`, `r  s3model2sum$coeff[5,1] + 1.96 * s3model2sum$coeff[5,2]`], t(390)=`r s3model2sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model2sum$coeff[5,3]),390))`)

Sad (b=`r s3model3sum$coeff[5,1]` [`r s3model3sum$coeff[5,1] - 1.96 * s3model3sum$coeff[5,2]`, `r s3model3sum$coeff[5,1] + 1.96 * s3model3sum$coeff[5,2]`], t(390)=`r s3model3sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model3sum$coeff[5,3]),390))`)

Anger (b=`r s3model4sum$coeff[5,1]` [`r s3model4sum$coeff[5,1] - 1.96 * s3model4sum$coeff[5,2]`, `r s3model4sum$coeff[5,1] + 1.96 * s3model4sum$coeff[5,2]`], t(390)=`r s3model4sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model4sum$coeff[5,3]),390))`)

Disgust (b=`r s3model5sum$coeff[5,1]` [`r s3model5sum$coeff[5,1] - 1.96 * s3model5sum$coeff[5,2]`, `r s3model5sum$coeff[5,1] + 1.96 * s3model5sum$coeff[5,2]`], t(390)=`r s3model5sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model5sum$coeff[5,3]),390))`)

Disappointment (b=`r s3model6sum$coeff[5,1]` [`r s3model6sum$coeff[5,1] - 1.96 * s3model6sum$coeff[5,2]`, `r s3model6sum$coeff[5,1] + 1.96 * s3model6sum$coeff[5,2]`], t(390)=`r s3model6sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model6sum$coeff[5,3]),390))`)

Surprise (b=`r s3model7sum$coeff[5,1]` [`r s3model7sum$coeff[5,1] - 1.96 * s3model7sum$coeff[5,2]`, `r s3model7sum$coeff[5,1] + 1.96 * s3model7sum$coeff[5,2]`], t(390)=`r s3model7sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model7sum$coeff[5,3]),390))`)

Fear (b=`r s3model8sum$coeff[5,1]` [`r s3model8sum$coeff[5,1] - 1.96 * s3model8sum$coeff[5,2]`, `r s3model8sum$coeff[5,1] + 1.96 * s3model8sum$coeff[5,2]`], t(390)=`r s3model8sum$coeff[5,3]` , p=`r 2*(1-pt(abs(s3model8sum$coeff[5,3]),390))`)



##### Simple Effects
Happy (b=`r s3model1sum$coeff[3,1]` [`r s3model1sum$coeff[3,1] - 1.96 * s3model1sum$coeff[3,2]`, `r s3model1sum$coeff[3,1] + 1.96 * s3model1sum$coeff[3,2]`], t(390)=`r s3model1sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model1sum$coeff[3,3]),390))`)

Content (b=`r s3model2sum$coeff[3,1]` [`r s3model2sum$coeff[3,1] - 1.96 * s3model2sum$coeff[3,2]`, `r s3model2sum$coeff[3,1] + 1.96 * s3model2sum$coeff[3,2]`], t(390)=`r s3model2sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model2sum$coeff[3,3]),390))`)

Sad (b=`r s3model3sum$coeff[3,1]` [`r s3model3sum$coeff[3,1] - 1.96 * s3model3sum$coeff[3,2]`, `r s3model3sum$coeff[3,1] + 1.96 * s3model3sum$coeff[3,2]`], t(390)=`r s3model3sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model3sum$coeff[3,3]),390))`)

Anger (b=`r s3model4sum$coeff[3,1]` [`r s3model4sum$coeff[3,1] - 1.96 * s3model4sum$coeff[3,2]`, `r s3model4sum$coeff[3,1] + 1.96 * s3model4sum$coeff[3,2]`], t(390)=`r s3model4sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model4sum$coeff[3,3]),390))`)

Disgust (b=`r s3model5sum$coeff[3,1]` [`r s3model5sum$coeff[3,1] - 1.96 * s3model5sum$coeff[3,2]`, `r s3model5sum$coeff[3,1] + 1.96 * s3model5sum$coeff[3,2]`], t(390)=`r s3model5sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model5sum$coeff[3,3]),390))`)

Disappointment (b=`r s3model6sum$coeff[3,1]` [`r s3model6sum$coeff[3,1] - 1.96 * s3model6sum$coeff[3,2]`, `r s3model6sum$coeff[3,1] + 1.96 * s3model6sum$coeff[3,2]`], t(390)=`r s3model6sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model6sum$coeff[3,3]),390))`)

Surprise (b=`r s3model7sum$coeff[3,1]` [`r s3model7sum$coeff[3,1] - 1.96 * s3model7sum$coeff[3,2]`, `r s3model7sum$coeff[3,1] + 1.96 * s3model7sum$coeff[3,2]`], t(390)=`r s3model7sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model7sum$coeff[3,3]),390))`)

Fear (b=`r s3model8sum$coeff[3,1]` [`r s3model8sum$coeff[3,1] - 1.96 * s3model8sum$coeff[3,2]`, `r s3model8sum$coeff[3,1] + 1.96 * s3model8sum$coeff[3,2]`], t(390)=`r s3model8sum$coeff[3,3]` , p=`r 2*(1-pt(abs(s3model8sum$coeff[3,3]),390))`)


## With Future
##### Interactions
Happy (b=`r s3model1sum$coeff[6,1]` [`r s3model1sum$coeff[6,1] - 1.96 * s3model1sum$coeff[6,2]`, `r s3model1sum$coeff[6,1] + 1.96 * s3model1sum$coeff[6,2]`], t(390)=`r s3model1sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model1sum$coeff[6,3]),390))`)

Content (b=`r s3model2sum$coeff[6,1]` [`r s3model2sum$coeff[6,1] - 1.96 * s3model2sum$coeff[6,2]`, `r  s3model2sum$coeff[6,1] + 1.96 * s3model2sum$coeff[6,2]`], t(390)=`r s3model2sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model2sum$coeff[6,3]),390))`)

Sad (b=`r s3model3sum$coeff[6,1]` [`r s3model3sum$coeff[6,1] - 1.96 * s3model3sum$coeff[6,2]`, `r s3model3sum$coeff[6,1] + 1.96 * s3model3sum$coeff[6,2]`], t(390)=`r s3model3sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model3sum$coeff[6,3]),390))`)

Anger (b=`r s3model4sum$coeff[6,1]` [`r s3model4sum$coeff[6,1] - 1.96 * s3model4sum$coeff[6,2]`, `r s3model4sum$coeff[6,1] + 1.96 * s3model4sum$coeff[6,2]`], t(390)=`r s3model4sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model4sum$coeff[6,3]),390))`)

Disgust (b=`r s3model5sum$coeff[6,1]` [`r s3model5sum$coeff[6,1] - 1.96 * s3model5sum$coeff[6,2]`, `r s3model5sum$coeff[6,1] + 1.96 * s3model5sum$coeff[6,2]`], t(390)=`r s3model5sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model5sum$coeff[6,3]),390))`)

Disappointment (b=`r s3model6sum$coeff[6,1]` [`r s3model6sum$coeff[6,1] - 1.96 * s3model6sum$coeff[6,2]`, `r s3model6sum$coeff[6,1] + 1.96 * s3model6sum$coeff[6,2]`], t(390)=`r s3model6sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model6sum$coeff[6,3]),390))`)

Surprise (b=`r s3model7sum$coeff[6,1]` [`r s3model7sum$coeff[6,1] - 1.96 * s3model7sum$coeff[6,2]`, `r s3model7sum$coeff[6,1] + 1.96 * s3model7sum$coeff[6,2]`], t(390)=`r s3model7sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model7sum$coeff[6,3]),390))`)

Fear (b=`r s3model8sum$coeff[6,1]` [`r s3model8sum$coeff[6,1] - 1.96 * s3model8sum$coeff[6,2]`, `r s3model8sum$coeff[6,1] + 1.96 * s3model8sum$coeff[6,2]`], t(390)=`r s3model8sum$coeff[6,3]` , p=`r 2*(1-pt(abs(s3model8sum$coeff[6,3]),390))`)



##### Simple Effects
Happy (b=`r s3model1sum$coeff[4,1]` [`r s3model1sum$coeff[4,1] - 1.96 * s3model1sum$coeff[4,2]`, `r s3model1sum$coeff[4,1] + 1.96 * s3model1sum$coeff[4,2]`], t(390)=`r s3model1sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model1sum$coeff[4,3]),390))`)

Content (b=`r s3model2sum$coeff[4,1]` [`r s3model2sum$coeff[4,1] - 1.96 * s3model2sum$coeff[4,2]`, `r s3model2sum$coeff[4,1] + 1.96 * s3model2sum$coeff[4,2]`], t(390)=`r s3model2sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model2sum$coeff[4,3]),390))`)

Sad (b=`r s3model3sum$coeff[4,1]` [`r s3model3sum$coeff[4,1] - 1.96 * s3model3sum$coeff[4,2]`, `r s3model3sum$coeff[4,1] + 1.96 * s3model3sum$coeff[4,2]`], t(390)=`r s3model3sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model3sum$coeff[4,3]),390))`)

Anger (b=`r s3model4sum$coeff[4,1]` [`r s3model4sum$coeff[4,1] - 1.96 * s3model4sum$coeff[4,2]`, `r s3model4sum$coeff[4,1] + 1.96 * s3model4sum$coeff[4,2]`], t(390)=`r s3model4sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model4sum$coeff[4,3]),390))`)

Disgust (b=`r s3model5sum$coeff[4,1]` [`r s3model5sum$coeff[4,1] - 1.96 * s3model5sum$coeff[4,2]`, `r s3model5sum$coeff[4,1] + 1.96 * s3model5sum$coeff[4,2]`], t(390)=`r s3model5sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model5sum$coeff[4,3]),390))`)

Disappointment (b=`r s3model6sum$coeff[4,1]` [`r s3model6sum$coeff[4,1] - 1.96 * s3model6sum$coeff[4,2]`, `r s3model6sum$coeff[4,1] + 1.96 * s3model6sum$coeff[4,2]`], t(390)=`r s3model6sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model6sum$coeff[4,3]),390))`)

Surprise (b=`r s3model7sum$coeff[4,1]` [`r s3model7sum$coeff[4,1] - 1.96 * s3model7sum$coeff[4,2]`, `r s3model7sum$coeff[4,1] + 1.96 * s3model7sum$coeff[4,2]`], t(390)=`r s3model7sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model7sum$coeff[4,3]),390))`)

Fear (b=`r s3model8sum$coeff[4,1]` [`r s3model8sum$coeff[4,1] - 1.96 * s3model8sum$coeff[4,2]`, `r s3model8sum$coeff[4,1] + 1.96 * s3model8sum$coeff[4,2]`], t(390)=`r s3model8sum$coeff[4,3]` , p=`r 2*(1-pt(abs(s3model8sum$coeff[4,3]),390))`)
```

